### 2021-06-11 README.Rmd
sfsfsfs

tibble(x = db_names, y = gsub("\n","",unlist(db_descript))) %>%
  mutate(x = str_sub(x, 1, nchar(x)-3)) %>%
  left_join(peacesciencer_functions, .) %>%
  mutate(func = paste0(x,"()")) -> peacesciencer_functions

peacesciencer_functions %>%
  mutate(link = paste0("[",x,"()](http://svmiller.com/peacesciencer/reference/",x,".html)")) -> peacesciencer_functions

>>>>

tibble(x = db_names, y = gsub("\n"," ",unlist(db_descript))) %>%
  mutate(x = str_sub(x, 1, nchar(x)-3)) %>%
  left_join(peacesciencer_functions, .) %>%
  mutate(func = paste0(x,"()")) -> peacesciencer_functions

peacesciencer_functions %>%
  mutate(link = paste0("[`",x,"()`](http://svmiller.com/peacesciencer/reference/",x,".html)")) -> peacesciencer_functions
